---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# healthgpsrvis

<!-- badges: start -->
[![R-CMD-check](https://github.com/imperialCHEPI/healthgpsrvis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/imperialCHEPI/healthgpsrvis/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `healthgpsrvis` is to plot and visualise data related to Health-GPS.

## Getting Started

### Prerequisites

- [RStudio](https://posit.co/download/rstudio-desktop/) installed
<!-- - [renv](https://rstudio.github.io/renv/) installed -->

### Installation

You can install the development version of `healthgpsrvis` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("imperialCHEPI/healthgpsrvis")
# devtools::install_github("imperialCHEPI/healthgpsrvis", ref = "branch-name")
```

## Example

This is an example to create the weighted data using the package:

```{r example}
library(healthgpsrvis)

# Get the path to the .rds file included in the testdata folder
filepath <- testthat::test_path("testdata", "data_ps3_reformulation")
#filepath <- "path/to/data.rds" # Get the path to the .rds file included in any other local folder


# Read the .rds file
data <- readRDS(filepath)

# Generate the weighted data
data_weighted <- gen_data_weighted(data)

# Generate the weighted data for the risk factors
data_weighted_rf_wide_collapse <- gen_data_weighted_rf(data_weighted)

# View structure of the weighted data for the risk factors
str(data_weighted_rf_wide_collapse)
```

To plot a risk factor (say, "bmi") for the weighted data, you can use the following code:

```{r riskfactor_plot}
# Plot the risk factor "bmi"
riskfactors("bmi", data_weighted)
```

To plot the difference in the risk factor (say, "bmi") for the weighted data, you can use the following code:

```{r riskfactors_diff_plot}
# Plot of difference in the risk factor "bmi"
riskfactors_diff("bmi", 
                 data_weighted_rf_wide_collapse,
                 scale_y_continuous_limits = c(-0.148, 0),
                 scale_y_continuous_breaks = c(-0.148, -0.074, 0),
                 scale_y_continuous_labels = c(-0.148, -0.074, 0))
```

To plot cumulative incidence difference for, say, "diabetes", you can use the following code:

```{r inc_cum_plot}
data_weighted_ds_wide_collapse <- gen_data_weighted_ds(data_weighted)
inc_cum("diabetes",
    data_weighted_ds_wide_collapse,
    scale_y_continuous_limits = c(-4424000, 0),
    scale_y_continuous_breaks = c(-4424000, -4084000, -3743000, -3403000, -3063000, -2722000, -2382000, -2042000, -1701000, -1361000, -1021000, -681000, -340000, 0),
    scale_y_continuous_labels = scales::comma(c(-4424000, -4084000, -3743000, -3403000, -3063000, -2722000, -2382000, -2042000, -1701000, -1361000, -1021000, -681000, -340000, 0))
  )
```

To plot burden of disease for, say, "yld", you can use the following code:

```{r burden_disease_plot}
data_weighted_bd_wide_collapse <- gen_data_weighted_burden(data_weighted)
burden_disease("yld", data_weighted_bd_wide_collapse)
```

<!--
### Cloning the Repository

```bash
git clone https://github.com/imperialCHEPI/healthgps-plots.git
cd healthgps-plots
```

### Setting Up the Project Environment with renv

1. Activate the renv environment:
```bash
Rscript -e 'renv::activate()'
```

2. Install project dependencies:
```bash
Rscript -e 'renv::restore()'
```

### Running the Script
You can now run the visualisation script using:
```bash
Rscript Visualisation.R path/to/HealthGPS_Result_S1.csv path/to/HealthGPS_Result_S2.csv path/to/HealthGPS_Result_S4.csv path/to/HealthGPS_Result_S5.csv
```

### Updating Dependencies
If you make changes to the project dependencies or want to ensure you have the latest versions, you can update the renv.lock file:
```bash
Rscript -e 'renv::snapshot()'
```

### Deactivating the renv Environment
After you are done using the project, you can deactivate the renv environment:
```bash
Rscript -e 'renv::deactivate()'
```
-->
